A weakly structured stem for human origins in Africa

### 2023-02-27 paper.tex
edits to methods

\sgcomment{Rough first pass for contributions:}
APR, BMH, and SG designed the study. BMH, EGA, EH, and MM designed and conducted 
participant recruitment.   APR, BMH, and SG designed statistical analyses.
APR conducted statistical analyses. 
APR, TDW, BMH, and SG interpreted the results and wrote the first draft of the article. 
All authors read and edited the article.

@@

\subsection*{Conditional site frequency spectrum}

>>>>

APR, BMH, and SG designed the study.
BMH, EGA, EH, and MM designed and conducted participant recruitment.
APR, BMH, and SG designed statistical analyses.
APR conducted statistical analyses. 
APR, TDW, BMH, and SG interpreted the results and wrote the first draft of the article. 
All authors read and edited the article.

@@

We used \texttt{Relate} \citep{Speidel2019-nj} to reconstruct genome-wide gene
genealogies from the retained populations in the merged ADRP and 1KGP datasets
(SI section~\ref{sec:relate}). From reconstructed genealogies, we computed
coalescence rates within and between populations, which provide an estimate for
effective population sizes over time and the relative cross-coalescence rates
between pairs of populations. To compare reconstructed genealogies from data to
model predictions, we used \texttt{msprime}
\citep{Kelleher2016-lw,Baumdicker2022-mj} to simulate genomic data for equal
numbers of samples for each population in our inferred models. We then applied
\texttt{Relate} to these simulated datasets using the same mutation and
recombination rates and generation time.
